Porting the Steel Bank Common Lisp Compiler and Runtime to the Nintendo Switch NX Platform

### 2025-05-19 els2025-sbcl-nx/presentation.tex
Fixup presentation code sample
Make figures fit.

\definecolor{bgcolor}{RGB}{255,240,240}
\definecolor{red}{RGB}{224,35,35}
\setbeamercolor{background canvas}{bg=bgcolor}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{titlelike}{fg=black}
\setbeamercolor{itemize item}{fg=red}
\setbeamercolor{enumerate item}{fg=red}
\setbeamertemplate{itemize items}[circle]
\setbeamertemplate{navigation symbols}{}
\usemintedstyle{monokai}
\newminted[lispcode]{common-lisp}{fontsize=\footnotesize}
\newminted[smalllispcode]{common-lisp}{fontsize=\scriptsize}
\def\code#1{{\color{codecolor}\texttt{#1}}}
\renewcommand{\theFancyVerbLine}{\color{darkgray}\large \oldstylenums{\arabic{FancyVerbLine}}}

@@

\begin{frame}
  \frametitle{Relocation example}
  XXX why doesn't this work?
%   \begin{listing}
%     \begin{minted}[fontsize=\small]{lisp}
% (defun f ()
%   (cons '(42 . 1958) 'els2025))

%      \end{minted}
%   \caption{A Lisp function referencing the constants \code{'(42 . 1958)} and \code{'ELS2025}.}
%   \label{lst:function}
%   \end{listing}
\end{frame}

\begin{frame}
  \frametitle{Relocation example (cont.)}
  \begin{figure}[h]
    \centering
    \includesvg[width=\linewidth]{Code object before shrinkwrapping.drawio.svg}
    \caption{Representation of the compiled code object (in boldface)
      for the function \protect\texttt{\#'f} in memory, along with the
      cons and symbol objects it references.}
    \label{fig:before-shrinkwrap}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Relocation example (cont.)}
  \begin{figure}[h]
    \centering
    \includesvg[width=\linewidth]{Code objects in memory after shrinkwrapping.drawio.svg}
    \caption{Representation of the same code object and the cons and
      symbol objects it references after code/data segregation and the
      rest of the shrinkwrapping process.}
    \label{fig:after-shrinkwrap}
  \end{figure}
\end{frame}

>>>>

\definecolor{bgcolor}{RGB}{255,240,240}
\definecolor{red}{RGB}{224,35,35}
\setbeamercolor{background canvas}{bg=bgcolor}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{titlelike}{fg=black}
\setbeamercolor{itemize item}{fg=red}
\setbeamercolor{enumerate item}{fg=red}
\setbeamertemplate{itemize items}[circle]
\setbeamertemplate{navigation symbols}{}
\newminted[lispcode]{common-lisp}{fontsize=\footnotesize}
\newminted[smalllispcode]{common-lisp}{fontsize=\scriptsize}
\def\code#1{{\color{codecolor}\texttt{#1}}}
\renewcommand{\theFancyVerbLine}{\color{darkgray}\large \oldstylenums{\arabic{FancyVerbLine}}}

@@

\begin{frame}[fragile]
  \frametitle{Relocation example}
\begin{minted}[fontsize=\small]{common-lisp}
 (defun f ()
   (cons '(42 . 1958) 'els2025))
\end{minted}
  A Lisp function referencing the constants \code{'(42 . 1958)} and \code{'ELS2025}
\end{frame}

\begin{frame}
  \begin{figure}
    \begin{columns}
      \column{0.6\linewidth}
      \vspace{-2em}
      \phantom{123}
      \includesvg[scale=0.5]{Code object before
        shrinkwrapping.drawio.svg}
      \column{0.4\linewidth}
      Representation of the compiled code object (in boldface)
      for the function \protect\texttt{\#'f} in memory, along with the
      cons and symbol objects it references.
    \end{columns}
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
    \begin{columns}
      \column{0.7\linewidth}
      \vspace{-1.7em}
      \phantom{123}
      \includesvg[scale=0.5]{Code objects in memory after
        shrinkwrapping.drawio.svg}
      \column{0.4\linewidth}
      Representation of the same code object and the cons and
      symbol objects it references after code/data segregation and the
      rest of the shrinkwrapping process.
    \end{columns}
  \end{figure}
\end{frame}
